\LARGE\bf Bayesian selection of best subsets in high-dimensional regression

### 2019-04-10 Manuscript/Jin/Project2.tex
[1]. we change the tau into (log(p))^2 for the simulation study. [2]. I insert into hybrid part the temperature idea borrowed from simulated annealing alrogithm [3]. For the real data analysis, we consistently use that tau and temperature idea, and sceen out 500 genes, with mcsize 5000 to select genes related BRCA1.

\begin{table}[H]
  \centering
  \caption{Simulation study results based on $2,000$ replications; FDR (false discovery rate), TRUE\% (percentage of the true model detected), SIZE (selected model size), HAM (Hamming distance), and s.e. (standard error).}\label{T:sim1}
  \begin{tabular}{cc|c|c|c|c}
    \hline
    Scenario&Method&FDR  (s.e.) & TRUE\% (s.e.) & SIZE (s.e.) & HAM (s.e.)  \\
    \hline
i&Proposed & 0.016 (0.001) & 92.600 (0.585)& 4.087 (0.007) & 0.087 (0.007) \\ 
    &SCAD & 0.034 (0.002) &  85.200 (0.794) & 4.188 (0.011) & 0.188 (0.011)\\ 
   &MCP & 0.035 (0.002) & 84.750 (0.804) & 4.191 (0.011) & 0.191 (0.011)\\ 
  &ENET & 0.016 (0.001) & 92.700 (0.582) & 4.087 (0.007) & 0.087 (0.007)\\ 
  &LASSO & 0.020 (0.002) & 91.350 (0.629) & 4.109 (0.009) & 0.109 (0.009)\\
    \hline
    ii&Proposed & 0.030 (0.002) & 86.250 (0.770) & 4.034 (0.007) & 0.236 (0.014)   \\
&SCAD & 0.059 (0.003) & 74.150 (0.979) & 4.107 (0.015) & 0.480 (0.022) \\ 
  &MCP & 0.137 (0.004) & 55.400 (1.112) & 4.264 (0.020) & 1.098 (0.034) \\ 
  &ENET & 0.501 (0.004) & 0.300 (0.122) & 7.716 (0.072) & 5.018 (0.052) \\ 
  &LASSO & 0.276 (0.004) & 15.550 (0.811) & 5.308 (0.033) & 2.038 (0.034) \\ 
    \hline
    iii&Proposed&0.014 (0.001) & 93.450 (0.553) & 4.073 (0.007) & 0.073 (0.007)\\
&SCAD & 0.027 (0.002) & 87.900 (0.729) & 4.145 (0.010) & 0.145 (0.010) \\ 
  &MCP & 0.031 (0.002) & 86.550 (0.763) & 4.172 (0.013) & 0.172 (0.013) \\ 
  &ENET & 0.035 (0.002) & 84.850 (0.802) & 4.181 (0.013) & 0.206 (0.012) \\ 
  &LASSO & 0.014 (0.001) & 93.850 (0.537) & 4.073 (0.007) & 0.073 (0.007) \\ 
    \hline
    iv&Proposed&0.032 (0.002) & 86.700 (0.759) & 4.051 (0.007) & 0.236 (0.015) \\
&SCAD & 0.068 (0.003) & 74.250 (0.978) & 4.196 (0.014) & 0.493 (0.023) \\ 
  &MCP & 0.152 (0.004) & 53.750 (1.115) & 4.226 (0.017) & 1.202 (0.035) \\ 
  &ENET & 0.417 (0.005) & 0.150 (0.087) & 6.228 (0.068) & 4.089 (0.043) \\ 
  &LASSO & 0.265 (0.004) & 19.500 (0.886) & 5.139 (0.029) & 1.909 (0.035) \\ 
    \hline
  \end{tabular}
\end{table}

>>>>

\begin{table}[H]
  \centering
  \caption{Simulation study results based on $2,000$ replications; FDR (false discovery rate), TRUE\% (percentage of the true model detected), SIZE (selected model size), HAM (Hamming distance), and s.e. (standard error).}\label{T:sim1}
  \begin{tabular}{cc|c|c|c|c}
    \hline
    Scenario&Method&FDR  (s.e.) & TRUE\% (s.e.) & SIZE (s.e.) & HAM (s.e.)  \\
    \hline
i&Proposed & 0.016 (0.001) & 92.600 (0.585)& 4.087 (0.007) & 0.087 (0.007) \\ 
&\textcolor{red}{local(new)}& 0.01(0.001) & 96.90 (0.388) & 4.03  (0.004) & 0.03 (0.004) \\
&\textcolor{red}{Proposed(new)} & 0.006 (0.001)& 96.900 (0.388) & 4.032(0.004) & 0.032 (0.004) \\
    &SCAD & 0.034 (0.002) &  85.200 (0.794) & 4.188 (0.011) & 0.188 (0.011)\\ 
   &MCP & 0.035 (0.002) & 84.750 (0.804) & 4.191 (0.011) & 0.191 (0.011)\\ 
  &ENET & 0.016 (0.001) & 92.700 (0.582) & 4.087 (0.007) & 0.087 (0.007)\\ 
  &LASSO & 0.020 (0.002) & 91.350 (0.629) & 4.109 (0.009) & 0.109 (0.009)\\
    \hline
    ii&Proposed & 0.030 (0.002) & 86.250 (0.770) & 4.034 (0.007) & 0.236 (0.014)   \\
    &\textcolor{red}{local(new)}& 0.03  (0.002) &  86.15  (0.773) & 3.99 (0.007) & 0.25  (0.015)\\
    &\textcolor{red}{Proposed(new)}& 0.023  (0.002) & 88.750  (0.707) & 3.985  (0.006) & 0.203 (0.014) \\
&SCAD & 0.059 (0.003) & 74.150 (0.979) & 4.107 (0.015) & 0.480 (0.022) \\ 
  &MCP & 0.137 (0.004) & 55.400 (1.112) & 4.264 (0.020) & 1.098 (0.034) \\ 
  &ENET & 0.501 (0.004) & 0.300 (0.122) & 7.716 (0.072) & 5.018 (0.052) \\ 
  &LASSO & 0.276 (0.004) & 15.550 (0.811) & 5.308 (0.033) & 2.038 (0.034) \\ 
    \hline
    iii&Proposed&0.014 (0.001) & 93.450 (0.553) & 4.073 (0.007) & 0.073 (0.007)\\
    &\textcolor{red}{local(new)}& 0.00  (0.001)  & 98.10  (0.305) & 4.02  (0.003)& 0.02(0.003)\\
    &\textcolor{red}{Proposed(new)} & 0.004(0.001)& 98.100 (0.305) & 4.020(0.003) & 0.020 (0.003) \\ 
&SCAD & 0.027 (0.002) & 87.900 (0.729) & 4.145 (0.010) & 0.145 (0.010) \\ 
  &MCP & 0.031 (0.002) & 86.550 (0.763) & 4.172 (0.013) & 0.172 (0.013) \\ 
  &ENET & 0.035 (0.002) & 84.850 (0.802) & 4.181 (0.013) & 0.206 (0.012) \\ 
  &LASSO & 0.014 (0.001) & 93.850 (0.537) & 4.073 (0.007) & 0.073 (0.007) \\ 
    \hline
    iv&Proposed&0.032 (0.002) & 86.700 (0.759) & 4.051 (0.007) & 0.236 (0.015) \\
    &\textcolor{red}{local(new)}& 0.04  (0.002)  & 85.30  (0.792) & 4.02  (0.006) & 0.28  (0.016) \\ 
     &\textcolor{red}{Proposed(new)}& 0.023(0.002)& 89.850 (0.675) & 4.005  (0.005 )& 0.190 (0.013) \\ 
&SCAD & 0.068 (0.003) & 74.250 (0.978) & 4.196 (0.014) & 0.493 (0.023) \\ 
  &MCP & 0.152 (0.004) & 53.750 (1.115) & 4.226 (0.017) & 1.202 (0.035) \\ 
  &ENET & 0.417 (0.005) & 0.150 (0.087) & 6.228 (0.068) & 4.089 (0.043) \\ 
  &LASSO & 0.265 (0.004) & 19.500 (0.886) & 5.139 (0.029) & 1.909 (0.035) \\ 
    \hline
  \end{tabular}
\end{table}
